Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/sec3-experiment-design.tex
删除一些错误
撰写R2Q1 & R2Q2的回复意见.

% added by wangyupan, 2020-12-21 ----start----
In sampled-based inference experiment, according to \cite{weihua2020_ogb-benchmark}, we used neighbor sampler \cite{hamilton2017_graphsage} with batch size of 1024 and all neighbors were inclued in all layers.
% added by wangyupan, 2020-12-21 ----end----

@@

    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time and memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})

          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
          %
          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

    \item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?} (Section~\ref{sec:training_time_breakdown})

          We decomposed the GNN training time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
          %
          On each level, we decomposed the training time of an epoch into several stages.
          %
          The most time-consuming stage was the performance bottleneck.
          %
          Optimizing its implementation will significantly reduce the training time.

@@

    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
          %
          Consequently, the training time and the memory usage should also decrease.
          %
          To validate effectiveness of sampling techniques, we measured the training time and peak memory usage under different batch sizes.
          %
          If sampling techniques were effective, they will be the keys to conduct GNN training on very big graphs.
          %
          If they were not effective, we want to find out which impairs its efficiency.
\end{itemize}

>>>>

@@

    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time, memory usage and accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})

          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
          %
          They also affect the accuracy of a GNN.
          %
          Larger hyper-parameter values usually mean more model parameters and more complex models.
          %
          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the accuracy on the test set changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

    \item[Q2] \emph{Which stage is the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})

          We decomposed the GNN training time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
          %
          On each level, we decomposed the training time of an epoch into several stages.
          %
          The most time-consuming stage was the performance bottleneck.
          %
          Optimizing its implementation will significantly reduce the training time.
          %
          For GNN inference, we conducted similar experimental analysis.
          %
          We discussed the differences in performance characteristics between training and inference.

@@

    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training? Does the use of sampling techniques in training affect the test accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training/inference of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The test accuracy of GNNs may also be affected.
          %
          To validate effectiveness of sampling techniques, we measured the training time, peak memory usage and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they will be the keys to conduct GNN training on very big graphs.
          %
          If they are not effective, we want to find out which impairs its efficiency.
          %

\end{itemize}
